Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-03 paper/main.tex
add Table with cummulative numbers

\begin{table}
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & \# formulas \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 404\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} \todo{RELEASE} & 376\\
Delag & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 397\\
Rabinizer & \todo ? & & 386\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Test: heatmap}
\centering
\begin{tabular}{c|ccccc|}
\multicolumn{1}{c}{} & 3 & 4 & 5 & 6 & \multicolumn{1}{c}{7} \\
%\specialrule{2pt}{0pt}{0pt}
\cline{2-6}
3 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \cellcolor{blue!25}\makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
4 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
5 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
6 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
7 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
\cline{2-6}
\end{tabular}
\end{table}

\begin{table}
\caption{Test: Data}
\centering
\begin{tabular}{cccccc}
\toprule
& & marks & \% red. & time & timeouts \\
\midrule
\multirow{4}{*}{\rotatebox[origin=c]{90}{\makecell{Delag \\ (420 marks)}}} & level 1 & 240 & 12.3 & 133.7 & 42 \\
& level 2 & 240 & 12.3 & 133.7 & 42 \\
& level 3 & 240 & 12.3 & 133.7 & 42 \\
& multilevel & 240 & 12.3 & 133.7 & 42 \\
\midrule
\multirow{4}{*}{\rotatebox[origin=c]{90}{\makecell{Rabinizer 4 \\ (420 marks)}}} & level 1 & 240 & 12.3 & 133.7 & 42 \\
& level 2 & 240 & 12.3 & 133.7 & 42 \\
& level 3 & 240 & 12.3 & 133.7 & 42 \\
& multilevel & 240 & 12.3 & 133.7 & 42 \\
\bottomrule
\end{tabular}
\end{table}

\begin{tikzpicture}
\begin{axis}[
	ymode=log,
	height=5cm,
	width=10cm,
	grid=major,
]
\addplot coordinates {
	(1, 0.3)
	(2, 0.8)
	(3, 1.5)
	(4, 2.7)
	(5, 3.9)
	(6, 4.1)
};
\addlegendentry{Delag}
\end{axis}
\end{tikzpicture}

>>>>

For each automata set (that is, the output of individual LTL translator), we
have run \telatko with various reduction levels, always with the incremental
solving turned on. We have again filtered out the automata for which any run
of \telatko timed out after 120 seconds. We do this to make sure the numbers
of acceptance marks can be meaningfully compared between different reduction
levels of the same automata set.

Table~\ref{tab:cumm-data} shows the number of marks in the input sets and after
each reduction level, together with the reduction ratio and time spent by the
individual reduction level. The columns \textit{solver response} and
\textit{solver timeout} show the number of automata for which the last query to
QBF solver has been successfully answered, or the solver timed out within a 30
seconds limit to a single query, respectively. An unanswered QBF formula (i.e.
the solver timed out) is considered unsatisfiable.

\begin{table}[h]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & \# formulas \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 404\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} \todo{RELEASE} & 376\\
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 397\\
\texttt{ltl2dgra} & 21.0 & & 386\\
\bottomrule
\end{tabular}
\end{table}

%\begin{table}[t]
%\centering
%\begin{tabular}{c|ccccc|}
%\multicolumn{1}{c}{} & 3 & 4 & 5 & 6 & \multicolumn{1}{c}{7} \\
%%\specialrule{2pt}{0pt}{0pt}
%\cline{2-6}
%3 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \cellcolor{blue!25}\makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
%4 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
%5 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
%6 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
%7 & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} & \makecell{\tiny{12} \\ \tiny{34}} \\
%\cline{2-6}
%\end{tabular}
%\end{table}

\begin{table}[h]
\caption{The cummulative number of acceptance marks before and after reduction
for various automata sets. \textit{X/Y solved aut.} means that out of
\textit{Y} successfully translated LTL formulas, every run of \telatko ended
within 120 seconds time limit on \textit{X} automata. We sum up the acceptance
marks only on these automata. The columns \textit{solver response} and
\textit{solver timeout} refer to last call to the QBF solver (that is, the
numbers of its successful responses within 30 seconds limit and timeouts).
}
\label{tab:cumm-data}
\centering
\input{table-data.tex}
\end{table}

%\begin{tikzpicture}
%\begin{axis}[
%	ymode=log,
%	height=5cm,
%	width=10cm,
%	grid=major,
%]
%\addplot coordinates {
%	(1, 0.3)
%	(2, 0.8)
%	(3, 1.5)
%	(4, 2.7)
%	(5, 3.9)
%	(6, 4.1)
%};
%\addlegendentry{Delag}
%\end{axis}
%\end{tikzpicture}
